---
title: "eda"
author: "Wei Wang (David)"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, comment = ' ')
pacman::p_load(tidyverse, ggplot2)
```

### Analysis goals
- PID distributions of the sample, 08-24
- Line chart of Democratic and Republican feeling thermometer ratings, 08-24 (`dem_therm` and `rep_therm`; weighted means)
  + Four lines * two panels: Full sample, Dem respondents, Rep respondents, Ind respondents
  + Run the same analysis for with `dem_liking_cses` and `rep_liking_cses` as robustness
- Stacked bar charts of non-responses
  + Also: broken down over time (clustered stacked bar chart)

```{r}
# load data
data <- read_csv('data/data.csv')
```

### PID distributions of the sample, 08-24

```{r rawcount}
# plot raw sample size count by year and partisanship
data_pid7_count <- data %>%
  filter(!is.na(pid7)) %>%
  mutate(party = case_when(
    pid7 %in% 1:2 ~ 'Democrat',
    pid7 == 3 ~ 'Lean Democrat',
    pid7 == 4 ~ 'Independent',
    pid7 == 5 ~ 'Lean Republican',
    pid7 %in% 6:7 ~ 'Republican'
  )) %>%
  mutate(party = factor(party, levels = c(
    'Democrat', 'Lean Democrat', 'Independent', 'Lean Republican', 'Republican'))) %>%
  count(year, party)
plot_pid7_count <- data_pid7_count %>%
  ggplot(aes(x = factor(year), y = n, fill = party)) + 
  geom_col() +
  scale_fill_manual(values = c('Democrat' = '#2166ac',
                               'Lean Democrat' = '#5b9bd5',
                               'Independent' = 'gray60',
                               'Lean Republican' = '#d97862',
                               'Republican' = '#b2182b')) +
  labs(
    x = 'Year',
    y = 'Count',
    title = 'Sample size by year and partisanship',
    fill = 'Partisanship'
  ) +
  theme_minimal()
plot_pid7_count

ggsave('outputs/fig_eda_rawcount.png', plot_pid7_count, width = 7, height = 4.5, dpi = 300)
```

```{r proportions}
data_pid7_prop <- data_pid7_count %>%
  group_by(year) %>%
  mutate(prop = n/sum(n)) %>%
  ungroup()

plot_pid7_prop <- data_pid7_prop %>%
  ggplot(aes(x = factor(year), y = prop, fill = party)) + 
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c('Democrat' = '#2166ac',
                               'Lean Democrat' = '#5b9bd5',
                               'Independent' = 'gray60',
                               'Lean Republican' = '#d97862',
                               'Republican' = '#b2182b')) +
  labs(
    x = 'Year',
    y = 'Percentage',
    title = 'Partisanship distributions by year',
    fill = 'Partisanship'
  ) +
  theme_minimal()

plot_pid7_prop

ggsave('outputs/fig_eda_props.png', plot_pid7_prop, width = 7, height = 4.5, dpi = 300)
```

### Weighted mean feeling thermometer ratings, 08-24

```{r thermometer}
# function for calculating weighted means
func_therm_mean <- function(df, therm_var, subsam_label, filter_expr) {
  df %>%
    filter(!is.na(.data[[therm_var]]), !is.na(weight), {{ filter_expr }}) %>%
    group_by(year) %>%
    summarise(mean_therm = weighted.mean(.data[[therm_var]], weight), .groups = 'drop') %>%
    mutate(group = subsam_label)
}

# function for creating dataframe for plotting
therm_summary <- function(df, therm_var) {
  bind_rows(
    func_therm_mean(df, therm_var, 'Full sample', TRUE),
    func_therm_mean(df, therm_var, 'Democrats',   pid7 %in% 1:3),
    func_therm_mean(df, therm_var, 'Independents', pid7 == 4),
    func_therm_mean(df, therm_var, 'Republicans', pid7 %in% 5:7)
  ) %>%
    mutate(group = factor(group, levels = c('Full sample', 'Democrats', 'Independents', 'Republicans')))
}

# plotting function
therm_plot <- function(df, therm_var, title) {
  therm_summary(df, therm_var) |>
    ggplot(aes(x = year, y = mean_therm, color = group)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    scale_color_manual(values = c('Full sample' = 'gray10',
                                  'Democrats'   = '#2166ac',
                                  'Independents' = 'gray60',
                                  'Republicans' = '#b2182b')) +
    scale_x_continuous(breaks = c(2008, 2012, 2016, 2020, 2024)) +
    scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
    labs(title = title, 
         x = 'Year', 
         y = 'Mean thermometer rating \n (0-49 = Cold; 51-100 = Warm)', 
         color = 'Subsample') +
    theme_minimal()
}

plot_demtherm <- therm_plot(data, 'dem_therm', 'Feeling thermometer for the Democratic Party')
plot_reptherm <- therm_plot(data, 'rep_therm', 'Feeling thermometer for the Republican Party')
plot_demtherm
plot_reptherm

ggsave('outputs/fig_eda_demtherm.png', plot_demtherm, width = 7, height = 4.5, dpi = 300)
ggsave('outputs/fig_eda_reptherm.png', plot_reptherm, width = 7, height = 4.5, dpi = 300)
```

### Robustness: Weighted mean CSES liking ratings, 08-24

```{r}
# reuse dataframe functions for thermometer
# slight modifications to the plotting function
liking_plot <- function(df, therm_var, title) {
  therm_summary(df, therm_var) |>
    ggplot(aes(x = year, y = mean_therm, color = group)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    scale_color_manual(values = c('Full sample' = 'gray10',
                                  'Democrats'   = '#2166ac',
                                  'Independents' = 'gray60',
                                  'Republicans' = '#b2182b')) +
    scale_x_continuous(breaks = c(2008, 2012, 2016, 2020, 2024)) +
    scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
    labs(title = title, 
         x = 'Year', 
         y = 'Mean CSES liking rating \n (0 = Strongly dislike; 10 = Strongly like)', 
         color = 'Subsample') +
    theme_minimal()
}

plot_demlike <- liking_plot(data, 'dem_liking_cses', 'Liking for the Democratic Party (CSES)')
plot_replike <- liking_plot(data, 'rep_liking_cses', 'Liking for the Republican Party (CSES)')
plot_demlike
plot_replike

ggsave('outputs/fig_eda_demliking.png', plot_demlike, width = 7, height = 4.5, dpi = 300)
ggsave('outputs/fig_eda_repliking.png', plot_replike, width = 7, height = 4.5, dpi = 300)
```

### Distribution of nonresponses 

```{r}
# recode data first
recode_y <- function(bin, text) {
  text_present <- !is.na(text) & nchar(trimws(text)) > 0
  y <- rep(NA_integer_, length(bin))
  y[bin == 5]                  <- 'Did not reach open-ended question'
  y[bin == 1 & !text_present]  <- 'No response'
  y[bin == 1 &  text_present]  <- 'Responded'
  y[is.na(bin) == T]           <- 'NA for parent question'
  y
}

data$y_dem_like    <- recode_y(data$dem_like_binary,    data$dem_like)
data$y_dem_dislike <- recode_y(data$dem_dislike_binary, data$dem_dislike)
data$y_rep_like    <- recode_y(data$rep_like_binary,    data$rep_like)
data$y_rep_dislike <- recode_y(data$rep_dislike_binary, data$rep_dislike)

# prep df for plotting
data_na <- data %>%
  select(y_dem_like, y_dem_dislike, y_rep_like, y_rep_dislike) %>%
  pivot_longer(everything(), names_to = 'question', values_to = 'response') %>%
  count(question, response) %>%
  group_by(question) %>%
  mutate(prop = n/sum(n)) %>%
  ungroup() %>%
  mutate(
    question = factor(question,
                      level = c('y_dem_like', 'y_dem_dislike', 'y_rep_like', 'y_rep_dislike'),
                      labels = c('Dem like', 'Dem dislike', 'Rep like', 'Rep dislike')),
    response = factor(response,
                      levels = c('NA for parent question',
                                 'Did not reach open-ended question',
                                 'No response',
                                 'Responded'))
    )

# plot stacked bar chart
plot_na <- data_na %>%
  ggplot(aes(x = question, y = prop, fill = response)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c('Responded'                         = '#66bd63',
                              'No response'                        = 'gray35',
                              'Did not reach open-ended question'  = 'gray60',
                              'NA for parent question'             = 'gray80')) +
  geom_text(aes(label = scales::percent(prop, accuracy = 1)),
            position = position_stack(vjust = 0.5),
            size = 4, color = 'white', fontface = 'bold') +
  labs(x = NULL, y = 'Percentage', fill = NULL,
       title = 'Proportion of non-response by open-ended question') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = 'bottom')
plot_na

ggsave('outputs/fig_eda_na.png', plot_na)
```

