---
title: "Predicting Open-Ended Response"
author: "Group 15"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
  html_document:
    code_folding: show
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide", fig.width = 8, fig.height = 4,
                      cache = TRUE, message = FALSE, warning = FALSE)
options(scipen = 0, digits = 3)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(glmnet, coefplot, tidyverse, sandwich, lmtest)
```

\pagebreak

# Question {-}

> **What predicts having any likes/dislikes for either party?**
> Who are we including/excluding in the open-ended sample?

A respondent is **excluded** from the open-ended sample if either

* they answered "No" to the like/dislike screener (`*_binary == 5`), **or**
* they said "Yes" but provided no actual open-ended text (`*_binary == 1` *and*
  the text field is `NA`).

\pagebreak

# Data prep

```{r read}
setwd("/Users/yzhang/Desktop/r_projects/mdm_final")
rm(list = ls())   
pacman::p_load(glmnet, coefplot, tidyverse, sandwich, lmtest)

data <- read.csv("data.csv", header = TRUE, na.strings = c("", "NA"))
dim(data)
```

## Recode the four outcomes

For each like/dislike pair, the new 0/1 outcome is:

* **1** if `*_binary == 1` AND the text field is non-empty (gave usable text)
* **0** if `*_binary == 5` OR (`*_binary == 1` AND text is NA)
* **NA** if `*_binary` itself is NA (drop these rows later)

```{r recode-y}
recode_y <- function(bin, text) {
  text_present <- !is.na(text) & nchar(trimws(text)) > 0
  y <- rep(NA_integer_, length(bin))
  y[bin == 5]                  <- 0L
  y[bin == 1 & !text_present]  <- 0L
  y[bin == 1 &  text_present]  <- 1L
  y
}

data$y_dem_like    <- recode_y(data$dem_like_binary,    data$dem_like)
data$y_dem_dislike <- recode_y(data$dem_dislike_binary, data$dem_dislike)
data$y_rep_like    <- recode_y(data$rep_like_binary,    data$rep_like)
data$y_rep_dislike <- recode_y(data$rep_dislike_binary, data$rep_dislike)

sapply(data[, c("y_dem_like","y_dem_dislike","y_rep_like","y_rep_dislike")],
       table, useNA = "ifany")
```

## Drop columns that should never be predictors

We drop:

* IDs and the survey weight (not substantive predictors).
* The raw outcome components.
* `age_cohort` (collinear with `age`).
* Items not asked every year (`understand_issue`, `too_complicated`,
  `power_matters`, `dem_satis`) and items with high missingness
  (`dem_liking_cses`, `rep_liking_cses`, `therm_lib`, `therm_consv`).
  Keeping them would drop the analytic sample below 15,000 after `na.omit`.

```{r drop}
drop_cols <- c("caseid", "uniq_id", "weight",
               "dem_like_binary", "dem_dislike_binary",
               "rep_like_binary", "rep_dislike_binary",
               "dem_like", "dem_dislike", "rep_like", "rep_dislike",
               "age_cohort",
               "understand_issue", "too_complicated",
               "power_matters", "dem_satis",
               "dem_liking_cses", "rep_liking_cses",
               "therm_lib", "therm_consv")
data <- data[, !(names(data) %in% drop_cols)]
```

## Collapse multi-level ordinals

Per-level coefficients on 7-point scales are hard to read in a table, so we
collapse them. Out-of-range codes (DK / RF / 0 / 9) fall through to `NA` and
get dropped by `na.omit` later. The middle category is set as the reference
so coefficients read as "vs moderates / independents."

```{r collapse-ordinals}
collapse_7pt <- function(x, labels) {
  factor(dplyr::case_when(
    x %in% 1:3 ~ labels[1],
    x == 4     ~ labels[2],
    x %in% 5:7 ~ labels[3],
    TRUE       ~ NA_character_
  ), levels = c(labels[2], labels[1], labels[3]))   # middle first = reference
}

data$pid7     <- collapse_7pt(data$pid7,     c("Dem", "Ind", "Rep"))
data$ideology <- collapse_7pt(data$ideology, c("Lib", "Mod", "Con"))
data$dem_ideo <- collapse_7pt(data$dem_ideo, c("Lib", "Mod", "Con"))
data$rep_ideo <- collapse_7pt(data$rep_ideo, c("Lib", "Mod", "Con"))

data$educ7 <- factor(dplyr::case_when(
  data$educ7 %in% 1:2 ~ "NoHS",
  data$educ7 %in% 3:5 ~ "HS_SomeCol",
  data$educ7 %in% 6:7 ~ "BA_plus",
  TRUE                ~ NA_character_
), levels = c("HS_SomeCol", "NoHS", "BA_plus"))   # HS = reference
```

## Make `year` a factor and convert remaining categoricals

```{r factors}
data$year <- factor(data$year)

cont_vars <- c("age", "dem_therm", "rep_therm")
y_vars    <- c("y_dem_like", "y_dem_dislike", "y_rep_like", "y_rep_dislike")
cat_vars  <- setdiff(names(data), c(cont_vars, y_vars, "year"))

# already-factor columns pass through unchanged; numeric ones get factored
data[cat_vars] <- lapply(data[cat_vars],
                         function(z) if (is.factor(z)) z else factor(z))
```

## Listwise-delete missing predictors

```{r na-omit, results = TRUE}
data_full <- na.omit(data)
dim(data_full)

# Every outcome should have both 0s and 1s, every year should have substantial counts.
cat("\nClass distribution of each outcome:\n")
for (y in y_vars) {
  cat(sprintf("  %-15s ", y)); print(table(data_full[[y]]))
}
cat("\nYear counts:\n"); print(table(data_full$year))
```

\pagebreak


## Build X and Y

```{r make-XY, results = TRUE}
Y_dl <- data_full$y_dem_like

# RHS = everything except the four outcomes
rhs  <- setdiff(names(data_full), y_vars)
form <- as.formula(paste("~", paste(rhs, collapse = " + ")))
X    <- model.matrix(form, data = data_full)[, -1]   # drop intercept col
dim(X)
```

## Force `year` in via `penalty.factor`

```{r pf, results = TRUE}
pf <- ifelse(grepl("^year", colnames(X)), 0, 1)
sum(pf == 0)   # number of year dummies forced in (= 4 for 5 years)
```

## Run `cv.glmnet`

```{r cv-dl, results = TRUE}
set.seed(10)
fit.dl.cv <- cv.glmnet(X, Y_dl,
                       alpha          = 1,
                       family         = "binomial",
                       nfolds         = 10,
                       penalty.factor = pf)
plot(fit.dl.cv)
fit.dl.cv$lambda.min
fit.dl.cv$lambda.1se
```

## Extract selected variables at `lambda.1se`

```{r coef-dl, results = TRUE}
coef.dl <- extract.coef(fit.dl.cv, lambda = fit.dl.cv$lambda.1se)
coef.dl
var.dl  <- rownames(coef.dl)[-1]   # column names from model.matrix
```

## Refit with `glm` (relaxed LASSO) and apply clustered SEs

`model.matrix` produces names like `pid7Rep`, `race_eth5`. We map them back
to parent variable names to write the `glm` formula.

```{r relaxed-dl, results = TRUE}
parent_var <- function(cols, vars) {
  hits <- sapply(cols, function(cn) {
    m <- vars[startsWith(cn, vars)]
    if (length(m)) m[which.max(nchar(m))] else NA_character_
  })
  unique(na.omit(hits))
}

vars.dl <- parent_var(var.dl, names(data_full))
vars.dl <- union(vars.dl, "year")   # year is forced in regardless

f.dl <- as.formula(paste("y_dem_like ~", paste(vars.dl, collapse = " + ")))
fit.dl <- glm(f.dl, data = data_full, family = binomial)

V.dl <- sandwich::vcovCL(fit.dl, cluster = ~ year, type = "HC1")
coeftest(fit.dl, vcov. = V.dl)
```

\pagebreak

# Loop over all four outcomes

Same logic, wrapped in a function.

```{r run-all, results = TRUE}
run_one <- function(y_name, data_full, seed = 10) {
  Y    <- as.numeric(data_full[[y_name]])
  stopifnot(length(unique(Y)) == 2)   # fail loud if Y is constant

  rhs  <- setdiff(names(data_full), y_vars)
  form <- as.formula(paste("~", paste(rhs, collapse = " + ")))
  X    <- model.matrix(form, data = data_full)[, -1]
  pf   <- ifelse(grepl("^year", colnames(X)), 0, 1)

  set.seed(seed)
  cv <- cv.glmnet(X, Y, alpha = 1, family = "binomial",
                  nfolds = 10, penalty.factor = pf)

  coef.tab <- extract.coef(cv, lambda = cv$lambda.1se)
  vars     <- parent_var(rownames(coef.tab)[-1], names(data_full))
  vars     <- union(vars, "year")

  f   <- as.formula(paste(y_name, "~", paste(vars, collapse = " + ")))
  fit <- glm(f, data = data_full, family = binomial)
  V   <- sandwich::vcovCL(fit, cluster = ~ year, type = "HC1")

  list(cv = cv, fit = fit, vcov = V,
       coef_test  = coeftest(fit, vcov. = V),
       n          = nrow(data_full),
       lambda_1se = cv$lambda.1se,
       n_selected = nrow(coef.tab) - 1)
}

results <- lapply(y_vars, run_one, data_full = data_full)
names(results) <- y_vars

data.frame(outcome    = y_vars,
           n          = sapply(results, `[[`, "n"),
           lambda_1se = sapply(results, `[[`, "lambda_1se"),
           n_selected = sapply(results, `[[`, "n_selected"))
```

```{r cv-plots, fig.height = 6}
par(mfrow = c(2, 2))
for (y in y_vars) { plot(results[[y]]$cv); title(y, line = 2.5) }
par(mfrow = c(1, 1))
```

```{r print-tables, results = TRUE}
for (y in y_vars) {
  cat("\n----- ", y, " -----\n")
  print(results[[y]]$coef_test)
}
```

\pagebreak

# Robustness check: pooled outcome

A respondent is **in the open-ended sample** if they provided usable text on
*any* of the four items. One binary outcome instead of four; if the same
predictors fall out we have evidence the per-item models aren't picking up
item-specific noise.

```{r pooled, results = TRUE}
data_full$y_pooled <- as.integer(
  data_full$y_dem_like    == 1 |
  data_full$y_dem_dislike == 1 |
  data_full$y_rep_like    == 1 |
  data_full$y_rep_dislike == 1
)
table(data_full$y_pooled, useNA = "ifany")

Y_p   <- data_full$y_pooled
rhs_p <- setdiff(names(data_full), c(y_vars, "y_pooled"))
form_p <- as.formula(paste("~", paste(rhs_p, collapse = " + ")))
X_p   <- model.matrix(form_p, data = data_full)[, -1]
pf_p  <- ifelse(grepl("^year", colnames(X_p)), 0, 1)

set.seed(10)
fit.p.cv <- cv.glmnet(X_p, Y_p, alpha = 1, family = "binomial",
                      nfolds = 10, penalty.factor = pf_p)
plot(fit.p.cv)

coef.p <- extract.coef(fit.p.cv, lambda = fit.p.cv$lambda.1se)
coef.p

vars.p <- parent_var(rownames(coef.p)[-1], names(data_full))
vars.p <- union(vars.p, "year")

f.p   <- as.formula(paste("y_pooled ~", paste(vars.p, collapse = " + ")))
fit.p <- glm(f.p, data = data_full, family = binomial)
V.p   <- sandwich::vcovCL(fit.p, cluster = ~ year, type = "HC1")
coeftest(fit.p, vcov. = V.p)
```

\pagebreak

# Summary
Across all four per-item models and the pooled robustness check, four predictor families do most of the work.

`y_dem_like` is the simplest model (15 predictors): partisanship, ideology placement, thermometers, and education explain who articulates Democratic likes.

`y_dem_dislike` is the richest model (26 predictors), pulling in age, race, gender, marital status, and work status. Articulating dislike of Democrats appears to be more demographically structured than articulating likes.

`y_rep_like` (14 predictors) is dominated by partisanship and ideology — demographics drop out almost entirely. Whether someone can articulate Republican likes is essentially a function of political engagement.

`y_rep_dislike` (25 predictors) again brings in demographics, similar to y_dem_dislike.

Below are some general findings -

1. Education is the single most consistent variable. `educ7BA_plus` is positive and highly significant in all four per-item models and the pooled model, and `educ7NoHS` is consistently negative. Holding everything else constant, college-educated respondents are roughly 60% more likely (in odds-ratio terms) to provide usable open-ended text than the high-school-or-some-college reference group. 

2. Partisan strength matters more than direction. Both `pid7Dem` and `pid7Rep` show positive coefficients in most models, indicating that identifying with either party (versus pure independents, the reference) predicts response. 

3. Political knowledge / engagement variables are extremely strong. `party_diff2` ("yes there's a difference between the parties") has beta = 0.55–0.92 in every model — one of the largest selected effects. `party_more_consv2` (correctly identifying Republicans as more conservative) is also consistently positive. 

Beyond education, demographics matter most for the dislike outcomes:

1. Age is positive and significant for both dislike outcomes (beta = 0.013–0.016 per year): older respondents are more likely to articulate dislikes. It does not appear in either like model at lambda lse.

2. Gender is selected in three of four models. Women (`gender2`) are slightly less likely to give open-ended responses than men; the "other" category (`gender3`) shows large effects in opposite directions across items, but the small cell size warrants caution.

3. Race/ethnicity is selected for `y_dem_dislike` and `y_rep_dislike`. Asian (`race_eth3`) and Hispanic (`race_eth5`) respondents are consistently less likely to give open-ended responses than the white-non-Hispanic reference, all else equal.



