---
title: "Predicting Open-Ended Response"
author: "Group 15"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
  html_document:
    code_folding: show
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide", fig.width = 8, fig.height = 4,
                      cache = TRUE, message = FALSE, warning = FALSE)
options(scipen = 0, digits = 3)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(glmnet, coefplot, tidyverse, sandwich, lmtest)
```

\pagebreak

# Question {-}

> **What predicts having any likes/dislikes for either party?**
> Who are we including/excluding in the open-ended sample?

A respondent is **excluded** from the open-ended sample if either

* they answered "No" to the like/dislike screener (`*_binary == 5`), **or**
* they said "Yes" but provided no actual open-ended text (`*_binary == 1` *and*
  the text field is `NA`).

\pagebreak

# Data prep

```{r read}
pacman::p_load(glmnet, coefplot, tidyverse, sandwich, lmtest)
data <- read.csv("data/data.csv", header = TRUE, na.strings = c("", "NA"))
dim(data)
```

## Recode the four outcomes

For each like/dislike pair, the new 0/1 outcome is:

* **1** if `*_binary == 1` AND the text field is non-empty (gave usable text)
* **0** if `*_binary == 5` OR (`*_binary == 1` AND text is NA)
* **NA** if `*_binary` itself is NA (drop these rows later)

```{r recode-y}
recode_y <- function(bin, text) {
  text_present <- !is.na(text) & nchar(trimws(text)) > 0
  y <- rep(NA_integer_, length(bin))
  y[bin == 5]                  <- 0L
  y[bin == 1 & !text_present]  <- 0L
  y[bin == 1 &  text_present]  <- 1L
  y
}

data$y_dem_like    <- recode_y(data$dem_like_binary,    data$dem_like)
data$y_dem_dislike <- recode_y(data$dem_dislike_binary, data$dem_dislike)
data$y_rep_like    <- recode_y(data$rep_like_binary,    data$rep_like)
data$y_rep_dislike <- recode_y(data$rep_dislike_binary, data$rep_dislike)

sapply(data[, c("y_dem_like","y_dem_dislike","y_rep_like","y_rep_dislike")],
       table, useNA = "ifany")
```

## Drop columns that should never be predictors

We drop:

* IDs and the survey weight (not substantive predictors).
* The raw outcome components.
* `age_cohort` (collinear with `age`).
* Items not asked every year (`understand_issue`, `too_complicated`,
  `power_matters`, `dem_satis`) and items with high missingness
  (`dem_liking_cses`, `rep_liking_cses`, `therm_lib`, `therm_consv`).
  Keeping them would drop the analytic sample below 15,000 after `na.omit`.

```{r drop}
drop_cols <- c("caseid", "uniq_id", "weight",
               "dem_like_binary", "dem_dislike_binary",
               "rep_like_binary", "rep_dislike_binary",
               "dem_like", "dem_dislike", "rep_like", "rep_dislike",
               "age_cohort",
               "understand_issue", "too_complicated",
               "power_matters", "dem_satis",
               "dem_liking_cses", "rep_liking_cses",
               "therm_lib", "therm_consv")
data <- data[, !(names(data) %in% drop_cols)]
```

## Collapse multi-level ordinals

Per-level coefficients on 7-point scales are hard to read in a table, so we
collapse them. Out-of-range codes (DK / RF / 0 / 9) fall through to `NA` and
get dropped by `na.omit` later. The middle category is set as the reference
so coefficients read as "vs moderates / independents."

```{r collapse-ordinals}
collapse_7pt <- function(x, labels) {
  factor(dplyr::case_when(
    x %in% 1:3 ~ labels[1],
    x == 4     ~ labels[2],
    x %in% 5:7 ~ labels[3],
    TRUE       ~ NA_character_
  ), levels = c(labels[2], labels[1], labels[3]))   # middle first = reference
}

data$pid7     <- collapse_7pt(data$pid7,     c("Dem", "Ind", "Rep"))
data$ideology <- collapse_7pt(data$ideology, c("Lib", "Mod", "Con"))
data$dem_ideo <- collapse_7pt(data$dem_ideo, c("Lib", "Mod", "Con"))
data$rep_ideo <- collapse_7pt(data$rep_ideo, c("Lib", "Mod", "Con"))

data$educ7 <- factor(dplyr::case_when(
  data$educ7 %in% 1:2 ~ "NoHS",
  data$educ7 %in% 3:5 ~ "HS_SomeCol",
  data$educ7 %in% 6:7 ~ "BA_plus",
  TRUE                ~ NA_character_
), levels = c("HS_SomeCol", "NoHS", "BA_plus"))   # HS = reference
```

## Make `year` a factor and convert remaining categoricals

```{r factors}
data$year <- factor(data$year)

cont_vars <- c("age", "dem_therm", "rep_therm")
y_vars    <- c("y_dem_like", "y_dem_dislike", "y_rep_like", "y_rep_dislike")
cat_vars  <- setdiff(names(data), c(cont_vars, y_vars, "year"))

# already-factor columns pass through unchanged; numeric ones get factored
data[cat_vars] <- lapply(data[cat_vars],
                         function(z) if (is.factor(z)) z else factor(z))
```

## Listwise-delete missing predictors

```{r na-omit, results = TRUE}
data_full <- na.omit(data)
dim(data_full)

# Every outcome should have both 0s and 1s, every year should have substantial counts.
cat("\nClass distribution of each outcome:\n")
for (y in y_vars) {
  cat(sprintf("  %-15s ", y)); print(table(data_full[[y]]))
}
cat("\nYear counts:\n"); print(table(data_full$year))
```

\pagebreak


## Build X and Y

```{r make-XY, results = TRUE}
Y_dl <- data_full$y_dem_like

# RHS = everything except the four outcomes
rhs  <- setdiff(names(data_full), y_vars)
form <- as.formula(paste("~", paste(rhs, collapse = " + ")))
X    <- model.matrix(form, data = data_full)[, -1]   # drop intercept col
dim(X)
```

## Force `year` in via `penalty.factor`

```{r pf, results = TRUE}
pf <- ifelse(grepl("^year", colnames(X)), 0, 1)
sum(pf == 0)   # number of year dummies forced in (= 4 for 5 years)
```

## Run `cv.glmnet`

```{r cv-dl, results = TRUE}
set.seed(10)
fit.dl.cv <- cv.glmnet(X, Y_dl,
                       alpha          = 1,
                       family         = "binomial",
                       nfolds         = 10,
                       penalty.factor = pf)
plot(fit.dl.cv)
fit.dl.cv$lambda.min
fit.dl.cv$lambda.1se
```

## Extract selected variables at `lambda.1se`

```{r coef-dl, results = TRUE}
coef.dl <- extract.coef(fit.dl.cv, lambda = fit.dl.cv$lambda.1se)
coef.dl
var.dl  <- rownames(coef.dl)[-1]   # column names from model.matrix
```

## Refit with `glm` (relaxed LASSO) and apply clustered SEs

`model.matrix` produces names like `pid7Rep`, `race_eth5`. We map them back
to parent variable names to write the `glm` formula.

```{r relaxed-dl, results = TRUE}
parent_var <- function(cols, vars) {
  hits <- sapply(cols, function(cn) {
    m <- vars[startsWith(cn, vars)]
    if (length(m)) m[which.max(nchar(m))] else NA_character_
  })
  unique(na.omit(hits))
}

vars.dl <- parent_var(var.dl, names(data_full))
vars.dl <- union(vars.dl, "year")   # year is forced in regardless

f.dl <- as.formula(paste("y_dem_like ~", paste(vars.dl, collapse = " + ")))
fit.dl <- glm(f.dl, data = data_full, family = binomial)

V.dl <- sandwich::vcovCL(fit.dl, cluster = ~ year, type = "HC1")
coeftest(fit.dl, vcov. = V.dl)
```

\pagebreak

# Loop over all four outcomes

Same logic, wrapped in a function.

```{r run-all, results = TRUE}
run_one <- function(y_name, data_full, seed = 10) {
  Y    <- as.numeric(data_full[[y_name]])
  stopifnot(length(unique(Y)) == 2)   # fail loud if Y is constant

  rhs  <- setdiff(names(data_full), y_vars)
  form <- as.formula(paste("~", paste(rhs, collapse = " + ")))
  X    <- model.matrix(form, data = data_full)[, -1]
  pf   <- ifelse(grepl("^year", colnames(X)), 0, 1)

  set.seed(seed)
  cv <- cv.glmnet(X, Y, alpha = 1, family = "binomial",
                  nfolds = 10, penalty.factor = pf)

  coef.tab <- extract.coef(cv, lambda = cv$lambda.1se)
  vars     <- parent_var(rownames(coef.tab)[-1], names(data_full))
  vars     <- union(vars, "year")

  f   <- as.formula(paste(y_name, "~", paste(vars, collapse = " + ")))
  fit <- glm(f, data = data_full, family = binomial)
  V   <- sandwich::vcovCL(fit, cluster = ~ year, type = "HC1")

  list(cv = cv, fit = fit, vcov = V,
       coef_test  = coeftest(fit, vcov. = V),
       n          = nrow(data_full),
       lambda_1se = cv$lambda.1se,
       n_selected = nrow(coef.tab) - 1)
}

results <- lapply(y_vars, run_one, data_full = data_full)
names(results) <- y_vars

data.frame(outcome    = y_vars,
           n          = sapply(results, `[[`, "n"),
           lambda_1se = sapply(results, `[[`, "lambda_1se"),
           n_selected = sapply(results, `[[`, "n_selected"))
```

```{r cv-plots, fig.height = 6}
png("data/lasso_response_output/viz_cv_plots.png", width = 1200, height = 900, res = 150)
par(mfrow = c(2, 2))
plot(results[["y_dem_like"]]$cv);    title("Democrat favorability",    line = 2.5)
plot(results[["y_dem_dislike"]]$cv); title("Democrat animosity", line = 2.5)
plot(results[["y_rep_like"]]$cv);    title("Republican favorability",  line = 2.5)
plot(results[["y_rep_dislike"]]$cv); title("Republican animosity", line = 2.5)
par(mfrow = c(1, 1))
dev.off()
```

```{r print-tables, results = TRUE}
for (y in y_vars) {
  cat("\n----- ", y, " -----\n")
  print(results[[y]]$coef_test)
}
```

\pagebreak

# Robustness check: pooled outcome

A respondent is **in the open-ended sample** if they provided usable text on
*any* of the four items. One binary outcome instead of four; if the same
predictors fall out we have evidence the per-item models aren't picking up
item-specific noise.

```{r pooled, results = TRUE}
data_full$y_pooled <- as.integer(
  data_full$y_dem_like    == 1 |
  data_full$y_dem_dislike == 1 |
  data_full$y_rep_like    == 1 |
  data_full$y_rep_dislike == 1
)
table(data_full$y_pooled, useNA = "ifany")

Y_p   <- data_full$y_pooled
rhs_p <- setdiff(names(data_full), c(y_vars, "y_pooled"))
form_p <- as.formula(paste("~", paste(rhs_p, collapse = " + ")))
X_p   <- model.matrix(form_p, data = data_full)[, -1]
pf_p  <- ifelse(grepl("^year", colnames(X_p)), 0, 1)

set.seed(10)
fit.p.cv <- cv.glmnet(X_p, Y_p, alpha = 1, family = "binomial",
                      nfolds = 10, penalty.factor = pf_p)
plot(fit.p.cv)

coef.p <- extract.coef(fit.p.cv, lambda = fit.p.cv$lambda.1se)
coef.p

vars.p <- parent_var(rownames(coef.p)[-1], names(data_full))
vars.p <- union(vars.p, "year")

f.p   <- as.formula(paste("y_pooled ~", paste(vars.p, collapse = " + ")))
fit.p <- glm(f.p, data = data_full, family = binomial)
V.p   <- sandwich::vcovCL(fit.p, cluster = ~ year, type = "HC1")
coeftest(fit.p, vcov. = V.p)
```

\pagebreak

# Summary
Across all four per-item models and the pooled robustness check, four predictor families do most of the work.

`y_dem_like` is the simplest model (15 predictors): partisanship, ideology placement, thermometers, and education explain who articulates Democratic likes.

`y_dem_dislike` is the richest model (26 predictors), pulling in age, race, gender, marital status, and work status. Articulating dislike of Democrats appears to be more demographically structured than articulating likes.

`y_rep_like` (14 predictors) is dominated by partisanship and ideology — demographics drop out almost entirely. Whether someone can articulate Republican likes is essentially a function of political engagement.

`y_rep_dislike` (25 predictors) again brings in demographics, similar to y_dem_dislike.

Below are some general findings -

1. Education is the single most consistent variable. `educ7BA_plus` is positive and highly significant in all four per-item models and the pooled model, and `educ7NoHS` is consistently negative. Holding everything else constant, college-educated respondents are roughly 60% more likely (in odds-ratio terms) to provide usable open-ended text than the high-school-or-some-college reference group. 

2. Partisan strength matters more than direction. Both `pid7Dem` and `pid7Rep` show positive coefficients in most models, indicating that identifying with either party (versus pure independents, the reference) predicts response. 

3. Political knowledge / engagement variables are extremely strong. `party_diff2` ("yes there's a difference between the parties") has beta = 0.55–0.92 in every model — one of the largest selected effects. `party_more_consv2` (correctly identifying Republicans as more conservative) is also consistently positive. 

Beyond education, demographics matter most for the dislike outcomes:

1. Age is positive and significant for both dislike outcomes (beta = 0.013–0.016 per year): older respondents are more likely to articulate dislikes. It does not appear in either like model at lambda lse.

2. Gender is selected in three of four models. Women (`gender2`) are slightly less likely to give open-ended responses than men; the "other" category (`gender3`) shows large effects in opposite directions across items, but the small cell size warrants caution.

3. Race/ethnicity is selected for `y_dem_dislike` and `y_rep_dislike`. Asian (`race_eth3`) and Hispanic (`race_eth5`) respondents are consistently less likely to give open-ended responses than the white-non-Hispanic reference, all else equal.


# Visualizations (RM)

I will take Ying's work and create visualizations that are consistent format with the text mining work. I have also edited the code under the cross-validation plots to save pngs. All visualizations can be found at: "\data\lasso_response_output"

## Response vs nonresponse rate

```{r viz_response_rate, results='show', fig.width=8, fig.height=4}

response_data <- data.frame(
  Item = c("Dem likes", "Dem dislikes", "Rep likes", "Rep dislikes"),
  Responded = c(
    sum(data$y_dem_like    == 1, na.rm = TRUE),
    sum(data$y_dem_dislike == 1, na.rm = TRUE),
    sum(data$y_rep_like    == 1, na.rm = TRUE),
    sum(data$y_rep_dislike == 1, na.rm = TRUE)
  ),
  No_response = c(
    sum(data$y_dem_like    == 0, na.rm = TRUE),
    sum(data$y_dem_dislike == 0, na.rm = TRUE),
    sum(data$y_rep_like    == 0, na.rm = TRUE),
    sum(data$y_rep_dislike == 0, na.rm = TRUE)
  )
) %>%
  mutate(Total = Responded + No_response) %>%
  pivot_longer(cols = c(Responded, No_response),
               names_to = "Status", values_to = "Count") %>%
  mutate(Proportion = Count / Total)

p_response <- ggplot(response_data, 
                     aes(x = Item, y = Proportion, fill = Status)) +
  geom_col(position = "stack", width = 0.4) +
  geom_text(aes(label = paste0(round(Proportion * 100, 1), "%")),
            position = position_stack(vjust = 0.5),
            size = 3.5, color = "white", fontface = "bold") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("No response" = "gray80", 
                                "Responded"   = "steelblue")) +
  labs(title = "Response rates to open-ended questions on party favorability and animosity",
       x = "", y = "Proportion", fill = "") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid = element_blank())

p_response
ggsave("data/lasso_response_output/viz_response_rate.png",
       p_response, width = 8, height = 4, dpi = 300)
```
With all types of non-responses:

```{r}
data_raw <- read.csv("data/data.csv", header = TRUE, na.strings = c("", "NA"))

make_response_breakdown <- function(bin_var, text_var, label) {
  bin  <- data_raw[[bin_var]]
  text <- data_raw[[text_var]]
  text_present <- !is.na(text) & nchar(trimws(text)) > 0
  
  data.frame(
    Item   = label,
    Status = case_when(
      is.na(bin)                    ~ "NA for parent question",
      bin == 5                      ~ "Did not reach open-ended question",
      bin == 1 & !text_present      ~ "No response",
      bin == 1 &  text_present      ~ "Responded",
      TRUE                          ~ NA_character_
    )
  )
}

response_long <- bind_rows(
  make_response_breakdown("dem_like_binary",    "dem_like",    "Dem like"),
  make_response_breakdown("dem_dislike_binary", "dem_dislike", "Dem dislike"),
  make_response_breakdown("rep_like_binary",    "rep_like",    "Rep like"),
  make_response_breakdown("rep_dislike_binary", "rep_dislike", "Rep dislike")
) %>%
  filter(!is.na(Status)) %>%
  count(Item, Status) %>%
  group_by(Item) %>%
  mutate(Proportion = n / sum(n)) %>%
  ungroup() %>%
  mutate(
    Item   = factor(Item, levels = c("Dem like", "Dem dislike", 
                                      "Rep like", "Rep dislike")),
    Status = factor(Status, levels = c(
      "NA for parent question",
      "No response",
      "Did not reach open-ended question",
      "Responded"
    ))
  )

p_response <- ggplot(response_long,
                     aes(x = Item, y = Proportion, fill = Status)) +
  geom_col(position = "stack", width = 0.4) +
  geom_text(aes(label = paste0(round(Proportion * 100), "%")),
            position = position_stack(vjust = 0.5),
            size = 3.5, color = "white", fontface = "bold") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c(
    "Responded"                          = "steelblue",
    "No response"                        = "gray40",
    "Did not reach open-ended question"  = "gray65",
    "NA for parent question"             = "gray85"
  )) +
  labs(title = "Proportion of non-response by open-ended question",
       x = "", y = "Percentage", fill = "") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        panel.grid = element_blank())

p_response
ggsave("data/lasso_response_output/viz_response_rate.png",
       p_response, width = 8, height = 5, dpi = 300)



```

```{r}
# Label lookup
term_labels <- c(
  "pid7Dem"           = "Party ID: Democrat",
  "pid7Rep"           = "Party ID: Republican",
  "ideologyLib"       = "Ideology: Liberal",
  "ideologyCon"       = "Ideology: Conservative",
  "dem_ideoLib"       = "Dem. party seen as: Liberal",
  "dem_ideoCon"       = "Dem. party seen as: Conservative",
  "rep_ideoLib"       = "Rep. party seen as: Liberal",
  "rep_ideoCon"       = "Rep. party seen as: Conservative",
  "party_diff2"       = "Parties are different (yes)",
  "party_diff9"       = "Parties are different (DK)",
  "party_more_consv2" = "Republicans more conservative (correct)",
  "party_more_consv9" = "Republicans more conservative (DK)",
  "right_track2"      = "Country on wrong track",
  "dem_therm"         = "Democrat thermometer",
  "rep_therm"         = "Republican thermometer",
  "age"               = "Age",
  "gender2"           = "Gender: Female",
  "gender3"           = "Gender: Other",
  "race_eth2"         = "Race: Black",
  "race_eth3"         = "Race: Asian",
  "race_eth4"         = "Race: Native American",
  "race_eth5"         = "Race: Hispanic",
  "race_eth6"         = "Race: Other",
  "educ7NoHS"         = "Education: No high school",
  "educ7BA_plus"      = "Education: College+",
  "marital_status2"   = "Marital: Widowed",
  "marital_status3"   = "Marital: Divorced/separated",
  "marital_status4"   = "Marital: Never married",
  "marital_status5"   = "Marital: Partnered",
  "work_status2"      = "Work: Part-time",
  "work_status3"      = "Work: Temporarily laid off",
  "work_status4"      = "Work: Unemployed",
  "work_status5"      = "Work: Retired",
  "health_insur2"     = "No health insurance",
  "reg_census2"       = "Region: Midwest",
  "reg_census3"       = "Region: South",
  "reg_census4"       = "Region: West"
)

apply_labels <- function(df) {
  df %>%
    mutate(term_label = ifelse(term %in% names(term_labels),
                               term_labels[term], term))
}

tidy_coeftest <- function(ct, outcome_name) {
  data.frame(
    term     = rownames(ct),
    estimate = ct[, 1],
    se       = ct[, 2],
    z        = ct[, 3],
    p        = ct[, 4],
    row.names = NULL
  ) %>%
    filter(!grepl("^\\(Intercept\\)|^year", term)) %>%
    mutate(
      outcome = outcome_name,
      lower   = estimate - 1.96 * se,
      upper   = estimate + 1.96 * se,
      sig     = ifelse(p < 0.05, "p < 0.05", "p >= 0.05")
    ) %>%
    apply_labels()
}

get_family <- function(term) {
  case_when(
    grepl("^pid7|^ideology|^dem_ideo|^rep_ideo", term) ~ "1_Partisanship/Ideology",
    grepl("^party_diff|^party_more|^right_track", term) ~ "2_Political Engagement",
    grepl("^dem_therm|^rep_therm", term) ~ "3_Thermometers",
    grepl("^age|^gender|^race_eth|^educ7|^marital|^work_status|^health|^sexori|^amer_parents|^relg", term) ~ "4_Demographics",
    grepl("^reg_census", term) ~ "5_Geography",
    TRUE ~ "6_Other"
  )
}

coef_all <- bind_rows(
  tidy_coeftest(results[["y_dem_like"]]$coef_test,    "Dem likes"),
  tidy_coeftest(results[["y_dem_dislike"]]$coef_test, "Dem dislikes"),
  tidy_coeftest(results[["y_rep_like"]]$coef_test,    "Rep likes"),
  tidy_coeftest(results[["y_rep_dislike"]]$coef_test, "Rep dislikes")
) %>%
  mutate(pred_family = get_family(term))
```

## Coefficient plots

Democrat outcomes coefficient plots:

```{r}

# Plot with family-based ordering
p_dem <- coef_all %>%
  filter(outcome %in% c("Dem likes", "Dem dislikes")) %>%
  arrange(pred_family, estimate) %>%
  mutate(term_label = factor(term_label, levels = unique(term_label))) %>%
  ggplot(aes(x = term_label, y = estimate, color = sig, shape = sig)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  coord_flip() +
  facet_wrap(~ outcome, scales = "free_y", ncol = 2) +
  scale_color_manual(values = c("p < 0.05" = "steelblue", "p >= 0.05" = "gray60")) +
  scale_shape_manual(values = c("p < 0.05" = 16, "p >= 0.05" = 1)) +
  labs(x = "", y = "Log-odds coefficient (clustered SE)", color = "", shape = "") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom",
        panel.spacing = unit(3, "cm"),
        axis.text.y = element_text(size = 7.5),
        strip.text = element_text(size = 10, face = "bold"))

p_dem
ggsave("data/lasso_response_output/viz_dem_coefs.png",
       p_dem, width = 14, height = 12, dpi = 300)
```

Republican outcomes coefficient plots:

```{r}
p_rep <- coef_all %>%
  filter(outcome %in% c("Rep likes", "Rep dislikes")) %>%
  arrange(pred_family, estimate) %>%
  mutate(term_label = factor(term_label, levels = unique(term_label))) %>%
  ggplot(aes(x = term_label, y = estimate, color = sig, shape = sig)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  coord_flip() +
  facet_wrap(~ outcome, scales = "free_y", ncol = 2) +
  scale_color_manual(values = c("p < 0.05" = "tomato", "p >= 0.05" = "gray60")) +
  scale_shape_manual(values = c("p < 0.05" = 16, "p >= 0.05" = 1)) +
  labs(x = "", y = "Log-odds coefficient (clustered SE)", color = "", shape = "") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom",
        panel.spacing = unit(3, "cm"),
        axis.text.y = element_text(size = 7.5),
        strip.text = element_text(size = 10, face = "bold"))

p_rep
ggsave("data/lasso_response_output/viz_rep_coefs.png",
       p_rep, width = 14, height = 12, dpi = 300)
```

Filtered to only top 10 terms:

```{r viz_coefs_top10, results='show', fig.width=12, fig.height=8}

# Filter to top 10 significant terms by absolute coefficient, per outcome
top10_coefs <- coef_all %>%
  filter(sig == "p < 0.05") %>%
  filter(!grepl("gender3", term)) %>%
  group_by(outcome) %>%
  arrange(desc(abs(estimate))) %>%
  slice_head(n = 10) %>%
  ungroup()

p_dem_top10 <- top10_coefs %>%
  filter(outcome %in% c("Dem likes", "Dem dislikes")) %>%
  mutate(term_label = reorder(term_label, estimate)) %>%
  ggplot(aes(x = term_label, y = estimate, color = outcome, shape = outcome)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  coord_flip() +
  facet_wrap(~ outcome, scales = "free_y", ncol = 2) +
  scale_color_manual(values = c("Dem likes" = "steelblue",
                                 "Dem dislikes" = "steelblue4")) +
  scale_shape_manual(values = c("Dem likes" = 16, "Dem dislikes" = 17)) +
  labs(title = "Top predictors of Democrat open-ended response",
       x = "", y = "Log-odds coefficient (clustered SE)",
       color = "", shape = "") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "none",
        panel.spacing = unit(2, "cm"),
        axis.text.y = element_text(size = 8),
        strip.text = element_text(size = 10, face = "bold"))

p_rep_top10 <- top10_coefs %>%
  filter(outcome %in% c("Rep likes", "Rep dislikes")) %>%
  mutate(term_label = reorder(term_label, estimate)) %>%
  ggplot(aes(x = term_label, y = estimate, color = outcome, shape = outcome)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  coord_flip() +
  facet_wrap(~ outcome, scales = "free_y", ncol = 2) +
  scale_color_manual(values = c("Rep likes" = "tomato",
                                 "Rep dislikes" = "tomato4")) +
  scale_shape_manual(values = c("Rep likes" = 16, "Rep dislikes" = 17)) +
  labs(title = "Top predictors of Republican open-ended response",
       x = "", y = "Log-odds coefficient (clustered SE)",
       color = "", shape = "") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "none",
        panel.spacing = unit(2, "cm"),
        axis.text.y = element_text(size = 8),
        strip.text = element_text(size = 10, face = "bold"))

p_dem_top10
p_rep_top10

ggsave("data/lasso_response_output/viz_dem_coefs_top10.png",
       p_dem_top10, width = 12, height = 6, dpi = 300)
ggsave("data/lasso_response_output/viz_rep_coefs_top10.png",
       p_rep_top10, width = 12, height = 6, dpi = 300)

```

## Year fixed effects

```{r}
# Extract year fixed effects from all four models
year_fe_ying <- bind_rows(
  lapply(y_vars, function(y) {
    ct <- results[[y]]$coef_test
    df <- data.frame(
      term     = rownames(ct),
      estimate = ct[, 1],
      se       = ct[, 2],
      z        = ct[, 3],
      p        = ct[, 4],
      row.names = NULL
    ) %>%
      filter(grepl("^year", term)) %>%
      mutate(
        outcome = y,
        term    = gsub("year", "", term),  # clean to just the year number
        stars   = case_when(
          p < 0.001 ~ "***",
          p < 0.01  ~ "**",
          p < 0.05  ~ "*",
          TRUE      ~ ""
        ),
        coef_fmt = paste0(round(estimate, 3), stars)
      )
  })
) %>%
  select(outcome, term, coef_fmt) %>%
  pivot_wider(names_from = term, values_from = coef_fmt) %>%
  rename(Outcome = outcome)

knitr::kable(year_fe_ying, 
             caption = "Year fixed effects — response models (ref = 2008, clustered SE)")
```

## Robustness check


```{r}
tidy_coeftest(coeftest(fit.p, vcov. = V.p), "Pooled") %>%
  filter(!grepl("gender3", term)) %>%
  mutate(pred_family = get_family(term)) %>% 
  arrange(pred_family, estimate) %>%
  mutate(term_label = factor(term_label, levels = unique(term_label))) %>%
  ggplot(aes(x = term_label, y = estimate, color = sig, shape = sig)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  coord_flip() +
  scale_color_manual(values = c("p < 0.05" = "darkgreen", "p >= 0.05" = "gray60")) +
  scale_shape_manual(values = c("p < 0.05" = 16, "p >= 0.055" = 1)) +
  labs(title = "Pooled outcome robustness check",
       x = "", y = "Log-odds coefficient (clustered SE)",
       color = "", shape = "") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom") -> p_pooled

p_pooled
ggsave("data/lasso_response_output/viz_pooled_coefs.png",
       p_pooled, width = 8, height = 7, dpi = 300)
```


